---
output: github_document
bibliography: pkg/vignettes/references.bib
---

# Overview

The **networkmeasures** package is implementing efficiency and vulnerability as metrics for assessing network complexity, e.g. traffic, family or business network. These metrics were first described by Latora et al [-@latora2001; -@latora2005] and Goldshtein et al [-@gol2004]. 

## Background

This package was developed during uRos the 2019 Unconf. We implemented:

1) The unweighted global efficieny measure for an igraph network (reference)
- naive implementation, using the average inverse shortest path between all the nodes
2) The unweighted local efficiency measure.

# Installation

You can install the development version from github, using the `remotes` package:

```{r eval=FALSE, include=TRUE}
remotes::install_github('uRosConf/networkmeasures/pkg', build_vignettes = TRUE)
```


# Usage

The vignette [introduction](pkg/doc/introduction.html) provides an intro to the functions and the theory behind them.

```{r eval=FALSE, include=TRUE}
vignette("introduction", package = "networkmeasures")
```

# References
