---
title: "Introduction to Network Measures"
author: "Mark van der Loo, Edwin de Jonge, Benjamin Schwetz"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{01_Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=FALSE}
library(networkmeasures)
```

### Introduction
This package is implementing metrics for assessing network complexity. It implements the following metrics: 

 *global network efficency * $E_{glob}$ as a metric to describe the small world behavior as first described by Latora et al (2001). For a Graph $G$, the network efficency E is calculated as:

$$ E_{glob}(G)~=~\frac{\sum_{i\neq j \in G^{\epsilon_{ij}}}}{N(N-1)}~=~\frac{1}{N(N-1)}\sum\limits_{i \neq j \in G} \frac{1}{d_{ij}} $$
Where $d_{ij}$ is the shortest path length between two points $i$ and $j$.

This measure is normalized, dividing it by the efficiency of the ideal network $G_{id}$, in which all possible $N(N-1)/2$ edges are present. Thus $0 \leq E(G) \leq 1$.


Efficiency can be assessed both globally (as above), and locally for the local subgraphs of the network. The *local efficiency* is then defined as the average efficiency of all subgraphs, i.e.

$$E_{loc}(G)~=~\frac{1}{N}\sum_{i \in G}E(G_i),~where  ~ i \notin G_i$$

In addition, *network vulnerability* as decribed by Latora et al (2005) is implemented. In a vulnearability anlysis, the goal is to investigate the impact of *attacks* or *improvements* of infrastructure components on the performance of the overall network. *Efficiency* is used as the metric for network performance. A vulnarability score each node $i$ in $G$, is computed as:

$$V(i)=1-\frac{E_{glob}(G_i)}{E_{glob}(G)}, ~where  ~ i \notin G_i$$

### Demo
We will be working with the `Koenigsberg` data set from the `igraphdata` package: A network of the 4 districts of Koenigsberg, connected by the 7 bridges of the city.  
```{r}
data("Koenigsberg", package = "igraphdata")
plot(Koenigsberg)
```
Using the shortest path
