---
title: "Introduction to Network Measures"
author: "Mark van der Loo, Edwin de Jonge, Benjamin Schwetz"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{01_Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, ,echo=FALSE}
library(networkmeasures)
library(igraph)
```

This package is implementing efficiency and vulnerability as metrics for assessing network complexity. These metrics were first described by Latora et al [-@latora2001; -@latora2005] and Goldshtein et al [-@gol2004]. 


# Efficiency

The network efficiency $E$ is desigend as a single metric to describe the small world behavior of a network. For a Graph $G$, the network efficency E is calculated as:

$$ E(G)~=~\frac{\sum_{i\neq j \in G^{\epsilon_{ij}}}}{N(N-1)}~=~\frac{1}{N(N-1)}\sum\limits_{i \neq j \in G} \frac{1}{d_{ij}} $$

Where $d_{ij}$ is the shortest path length between two points $i$ and $j$. It is normalized, by dividing with the efficiency of the ideal network $G_{id}$, in which all possible $N(N-1)/2$ edges are present. Thus $0 \leq E(G) \leq 1$.

To examplify the interpretation, we will use the `Koenigsberg` data set from the `igraphdata` package: It is the famous network of 7 bridges (edges) connecting the 4 districts (nodes) of the city Koenigsberg:  
```{r}
data("Koenigsberg", package = "igraphdata")
plot(Koenigsberg)
```

We can see that the quarters are very well connected: A bridge is only missing between `Altstadt-Loebenicht`and `Vorstadt_Haberberg`. Otherwise, the graph would be complete. We can calculate $E(G)$ using the `efficiency()` function: 
```{r}
efficiency(Koenigsberg)
```

As expected, we get a value close to the ideal of $1$. People were able to move around the city very efficiently, using the city's bridge system.


## Local efficiency

This idea is expanded to investigate local properties of the graph. We define $G_i$ as the subgraph of the neighbors of i. For the node `Altstadt-Loebenicht` this graph would simply be:

```{r echo=FALSE}
plot(make_ego_graph(Koenigsberg, order = 1, mindist = 1)[[1]])
```


The `local_efficiency()` function in this package, calculates the efficiency of the subgraph of each node $i$ in $G_i$: 
```{r}
local_efficiency(Koenigsberg)
```


## Global and Local efficiency as network metrics

Following Latora et al (2001), a local efficiency score $E_{loc}$ for the entire network $G$, can then be calculated as the mean efficiency of all subgraphs, i.e.

$$E_{loc}(G)~=~\frac{1}{N}\sum_{i \in G}E(G_i),~where  ~ i \notin G_i$$
```{r}
E_loc <- mean(local_efficiency(Koenigsberg))
```

Opposed to $E_{loc}$, the efficiency of the graph $E$ is labelled *global* efficiency $E_{glob}$. These two are close for graphs with small differences between the distances. This holds for our example of `Koenigsberg`, where they are in fact the same:

```{r}
E_glob <- efficiency(Koenigsberg)
data.frame(E_glob,E_loc)
```

$E_{glob}$ is the efficiency of a parallel system, while $E_{loc}$ is describing the efficiency of a sequential system. 


# Network vulnerability

In addition and building on the concept of efficiency, network vulnerability is implemented with the `vulnerability` function: In a vulnearability analysis, the goal is to investigate the impact of *attacks* or *improvements* of infrastructure components on the performance of the overall network. *Efficiency* is used as the metric for network performance. A vulnerability score for each node $i$ in $G$, is computed as:

$$V(i)=1-\frac{E(G_i)}{E(G)}, ~where  ~ i \notin G_i$$
What if the `Altstadt-Loebenicht` became impassable? The resulting network $G_i$ would be

```{r}
g_i <- delete_vertices(Koenigsberg, 1)
plot(g_i)
```

Using this package, the scores for`Koenigsberg` can be calculated: 

```{r}
vulnerability_nodes(Koenigsberg) #I'd say this makes more sense
```

We can see that `Kneiphof` and `Lomse` are the most vulnerable nodes. If they became impassable, there would be less options to travel between `Altstadt-Loebenicht`and `Vorstadt_Haberberg`. Mathematically, a destruction of the latter two would "improve" travelling in the city, as the remaining system of quarters and bridges would be a complete graph.

Using `vulnerability_edges`, we can make the same investigation for the edges in the graph:

```{r}
vulnerability_edges(Koenigsberg)
```
Where there are more than one bridge connecting the quarters, vulnerability is $0$. See below
```{r}
col_vec <- vulnerability_edges(Koenigsberg) %>% 
  map_chr(~if(.x == 0) "green" else "black")
plot(
  Koenigsberg,
  vertex.label = NA,
  edge.label = edge_attr(Koenigsberg)$name,
  edge.color = col_vec
)
```


# References


